---
title: "Extending to new text and other issue areas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Extending to new text and other issue areas}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

# Scoring new IPR paragraphs

```{r}
library(nteText)

new_paragraphs <- c(
  "Patent enforcement remains weak across multiple sectors. Counterfeit pharmaceuticals account for an estimated 30 percent of domestic sales.",
  "The country has fully implemented its TRIPS obligations and maintains robust enforcement mechanisms."
)
nte_score_ipr(
  text    = new_paragraphs,
  country = c("INDIA", "SINGAPORE"),
  year    = c(2020L, 2020L)
)
```

Each input requires a country and a year. Both are inserted into the
premise template the model was trained against, so passing accurate
metadata matters. Lower (more negative) scores indicate stronger
IPR-barrier rhetoric.

The first call downloads the model weights from Hugging Face Hub and
caches them locally, so subsequent calls are fast.

The scoring function targets IPR paragraphs only. The fine-tuned model
was trained on hypothesis labels specific to intellectual property
rights barriers. Applying it to paragraphs from other issue areas will
produce out-of-distribution outputs without any error or warning.

# Working with other issue areas without the model

For non-IPR sections, the package provides corpus exploration tools
that do not require any classifier.

```{r}
services <- nte_subset(issue = "SERVICES")

nte_kwic(services, keyword = "telecommunications", window = 10)

nte_term_trends(services,
  terms = c("digital", "data localization", "cross-border data"))

nte_wordcloud(
  services,
  group_a = country == "CHINA",
  group_b = country == "INDIA",
  top_n = 60
)

nte_compare_corpora(
  services,
  group_a = year >= 2015,
  group_b = year < 2010,
  measure = "chi2",
  top_n = 30
)
```

# Fine-tuning your own model for another issue area

The fine-tuning workflow that produced the IPR model lives in the
\code{NTE_DeBERTa_V3_revised_colab.ipynb} notebook in the source
repository. To extend hypothesis classification to another issue area,
run that notebook against a labeled training set for that area, push
the resulting checkpoint to Hugging Face Hub, and pass its identifier
to the \code{model_id} argument.

```{r}
nte_score_ipr(
  text    = services_paragraphs,
  country = services_countries,
  year    = services_years,
  model_id = "you/nte-deberta-services"
)
```

The function name keeps its IPR-only naming because the helper
hardcodes 13 IPR hypotheses and a min-max rescaling fitted to the
published IPR corpus. Adapting it to a different label schema requires
editing \code{inst/python/score_ipr.py} (replace the \code{HYPOTHESES}
list and the \code{PUBLISHED_RAW_MIN}/\code{PUBLISHED_RAW_MAX} bounds).
