---
title: "Introduction to nteText"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to nteText}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This package ships the section-level corpus from the United States Trade
Representative's annual National Trade Estimate reports along with
hypothesis-alignment scores for the intellectual property rights issue
area. The scores come from a DeBERTa-v3 classifier fine-tuned on the
hand-labeled training set described in Park (2026, working paper).

# Loading the corpus

```{r}
library(nteText)
corp <- nte_load()
dplyr::glimpse(corp)
```

# Subsetting to one issue area

```{r}
ipr <- nte_subset(corp, issue = "IPR")
nrow(ipr)
```

You can also filter to specific years or countries.

```{r}
nte_subset(corp, issue = "SERVICES", years = 2010:2020,
           countries = c("CHINA", "INDIA"))
```

# Bundled IPR scores

```{r}
scored <- nte_ipr_scored()
dplyr::glimpse(scored)
summary(scored$deberta_score)
```

# Quick exploration

```{r, eval = FALSE}
nte_kwic(ipr, keyword = "compulsory licensing", window = 10)

nte_term_trends(ipr,
  terms = c("geographical indication", "compulsory license"))

nte_country_profile("CHINA", data = ipr, plot = TRUE)
```
