---
title: "Replicating the published analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Replicating the published analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

The published analysis is fully reproducible from the data bundled with
this package. No Python is required at replication time because the
DeBERTa scores are pre-computed and shipped as \code{NTE_IPR_scored}.

# One-shot reproduction

```{r}
library(nteText)
nte_replicate_paper(dir = "replication_output")
```

This regenerates every figure and table in the manuscript and writes
PNG and TEX files to the supplied directory.

# Just the validation figures

```{r}
nte_validation_plots(dir = "validation_output")
```

# Re-deriving the IPR subset from the parent corpus

The bundled \code{NTE_IPR_scored} dataset is a paragraph-level slice
that adds DeBERTa scores. The corresponding section-level slice can be
re-derived from \code{NTEbysect} as follows.

```{r}
section_level_ipr <- nte_subset(issue = "IPR")
nrow(section_level_ipr)
```
